Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS

### 2023-06-16 paper/ms.tex
add 4029 appendix plot

\section{The LP 12-502 glitch}

Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247
from Figure~\ref{fig:lp}.

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
		\vspace{-0.45cm}
		\caption{
			LP 12-502 is wild.
		}
		\label{fig:lpzoom}
	\end{center}
\end{figure*}

>>>>

\section{LP 12-502}

{\it The light curve}---
Figure~\ref{fig:lplc} shows an alternative view of the LP-502 light
curve from Figure~\ref{fig:lp}, 
split into ``time chunks'' wherever there was more than half a day of
missing data in the TESS light curve.
We binned the light curve to 15-minute intervals for visual clarity,
and required at least one (120-second cadence) flux measurement per
bin.
Points more than 2.5$\sigma$ above the median are drawn in gray, also
for visual clarity.
Missing data are not drawn (a common plotting error when ``drawing''
light curves, rather than showing a scatter plot).

{\it State switches}---
Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247.

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{tic4029_segments.pdf}
		\vspace{-0.2cm}
		\caption{
			LP 12-502 light curve, split into time chunks.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
		\vspace{-0.45cm}
		\caption{
			LP 12-502 cycles 1233-1247, showing the most dramatic state
      change observed over the three year baseline.
		}
		\label{fig:lpzoom}
	\end{center}
\end{figure*}
